Scheduling and Amortization for MPC

### 2021-12-17 paper_SIMD.tex
Work in progress commit. Added handling of "mixed" def-use edges. Still need add raise_dim and drop_dim and handling of array accesses A[f(i)].

\ana{We need to double check that the following captures all cases of def-use edges.}
The dependence graph has the following def-use edges:

\begin{itemize}
\item same-level forward $X\rightarrow Y$ where $X$ and $Y$ are in the same loop nest $i_1,i_2,...i_k$. E.g., $\texttt{d} = \mathit{SUM}(\texttt{S}[i,j], \texttt{C}[j])$ to $\texttt{p} = \mathit{MUL}(\texttt{d},\texttt{d})$ in Biometric is a same-level edge. A $\phi$ node can be a source of a same-level forward edge but not a target. 
\item outer-to-inner forward $X\rightarrow Y$ where $X$ is in an outer loop nest, $i_1,i_2,...i_j$, and $Y$ is in an inner one, $i_1,i_2,...i_j,...,i_k$. A $\phi$-node can be a source or a target of an outer-to-inner forward edge. 
\item inner-to-outer forward $X\rightarrow Y$ where $X$ is a $phi$-node in an inner loop nest, $i_1,i_2,...i_k,i_{k+1}$, and $Y$ is in the enclosing loop nest $i_1,i_2,...i_k$. E.g. $\texttt{sum}_0 = \phi(\texttt{sum}_1, 0)$ to $\texttt{c} = \mathit{CMP}(\texttt{sum}_0,\texttt{min}_0)$ is an inner-to-outer forward edge. Note that the source is \emph{always} a $\phi$-node in the immediately enclosing loop. The interpretation of this edge is that the use node $Y$ uses the definition made in the last iteration of the inner loop. 
\item same-level back-edge $X\rightarrow Y$. $Y$ is a phi-node in the header of the loop and $X$ is a definition of the variable in the loop body. E.g., $\texttt{min}_1 = \mathit{MUX}(\texttt{c},\texttt{sum}_1,\texttt{min}_1)$ to $\texttt{min}_0 = \phi(\texttt{min}_1, 10000)$ in Biometric is a same-level back-edge. 
\item inner-to-outer back-edge $X\rightarrow Y$: $X$ and $Y$ are both $\phi$-nodes for some variable. The source $X$ is in a loop nest immediately nested into $Y$'s loop nest. 
 \end{itemize}

@@

\ana{Add back-edges into Phase 1. A back-edge from a non-phi-node in loop $i$ to a phi-node in loop $i$'s header is a same-level edge. The only difference with the handling of normal same-level forward def-use is that the operand index will become $i-1$. A back edge from a phi-node in loop $j$ to a phi-node in loop $i$, where $j$ is immediately nested in $i$ is an inner-to-outer edge and will require dropping dimension. We can show these are the only kinds of back-edges that may occur.}

@@

\STATE \COMMENT {Phase 1: Raise dimension of scalar variables to corresponding loop nest. We may assume linear traversal of the MPC-source. \ana{Double check!}}

@@

\subsubsection{Phase 1 of Vectorization algorithm:}

@@

\ana{Conjecture: Basic Vectorization still works with minor extensions and correctness argument still hods. }

>>>>

%\ana{We need to double check that the following captures all cases of def-use edges.}
The dependence graph has the following def-use edges:

\begin{itemize}
\item same-level forward $X\rightarrow Y$ where $X$ and $Y$ are in the same loop nest $i_1,i_2,...i_k$. E.g., $\texttt{d} = \mathit{SUM}(\texttt{S}[i,j], \texttt{C}[j])$ to $\texttt{p} = \mathit{MUL}(\texttt{d},\texttt{d})$ in Biometric is a same-level edge. A $\phi$ node can be a source of a same-level forward edge but not a target. 
\item outer-to-inner forward $X\rightarrow Y$ where $X$ is in an outer loop nest, $i_1,i_2,...i_j$, and $Y$ is in an inner one, $i_1,i_2,...i_j,...,i_k$. A $\phi$-node can be a source or a target of an outer-to-inner forward edge. 
\item inner-to-outer forward $X\rightarrow Y$ where $X$ is a $phi$-node in an inner loop nest, $i_1,i_2,...i_k,i_{k+1}$, and $Y$ is in the enclosing loop nest $i_1,i_2,...i_k$. E.g. $\texttt{sum}_0 = \phi(\texttt{sum}_1, 0)$ to $\texttt{c} = \mathit{CMP}(\texttt{sum}_0,\texttt{min}_0)$ is an inner-to-outer forward edge. Note that the source is \emph{always} a $\phi$-node in the immediately enclosing loop. The interpretation of this edge is that the use node $Y$ uses the definition made in the last iteration of the inner loop. 
\item same-level back-edge $X\rightarrow Y$. $Y$ is a phi-node in the header of the loop and $X$ is a definition of the variable in the loop body. E.g., $\texttt{min}_1 = \mathit{MUX}(\texttt{c},\texttt{sum}_1,\texttt{min}_1)$ to $\texttt{min}_0 = \phi(\texttt{min}_1, 10000)$ in Biometric is a same-level back-edge. 
\item inner-to-outer back-edge $X\rightarrow Y$: $X$ and $Y$ are both $\phi$-nodes for some variable. The source $X$ is in a loop nested into $Y$'s loop (not necessarily immediately).

\item mixed forward edge $X\rightarrow Y$. $X$ is a $phi$-node in some loop $i_1,i_2,...i_k,i_{k+1}$ and $Y$ is a node in a loop nested into $i_1,i_2,...i_k$. We transform mixed forward edges as follows. Let $\x_j$ be the variable defined at the phi-node $X$. We add a variable and assignment $\x'_j = \x_j$ immediately after the $i_1,i_2,...i_k$ loop. Then we replace the use of $\x_j$ at $Y$ with $\x'_j$. This transforms a mixed forward edge into an "inner-to-outer" forward edge followed by an outer-to-inner forward edge. Thus Basic Vectorization handles one of "same-level", "inner-to-outer", or "outer-to-inner" def-use edges.
 \end{itemize}

@@

\ana{Add back-edges into Phase 1. A back-edge from a non-phi-node in loop $i$ to a phi-node in loop $i$'s header is a same-level edge. The only difference with the handling of normal same-level forward def-use is that the operand index will become $i-1$. A back edge from a phi-node in loop $j$ to a phi-node in loop $i$, where $j$ is nested in $i$ is an inner-to-outer edge and will require dropping dimension. We can show these are the only kinds of back-edges that may occur.}

@@

\STATE \COMMENT {Phase 1: Raise dimension of scalar variables to corresponding loop nest. We may assume linear traversal of the MPC-source.}

@@

\subsubsection{Phase 1 of Basic Vectorization:}

@@
